---
# title: "Untitled"
# author: "Haziq Jamil"
# date: "12/12/2018"
header-includes:
   - \usepackage{subfig}
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(diagacc)
library(cowplot)
load("simresults.RData")
```


# Data generation

Haziq: could you please give below the steps that you use to generate
the data with the gold standard. I outline what I think it should be the
steps: Within each replication, the data are generated as follows:

***Haziq: This is correct. Note that I have now used MCMC (JAGS) as a method of fitting all models LC, LCRE and FM.***

1.  item class probabilities for six items (the sixth item is the gold
    standard that has sensitivity and specificity 1) and prevalence are
    set (2 latent classes are assumed).

2.  Posterior probabilities are computed for each respondent (n=250 or
    n=1000).

3.  Given the respondent’s latent class you generate the binary
    indicators for the six items. Unless there is 100% missigness of the
    gold standard in which case you only generate five items.

4.  After a data set is being generated, the three models are fitted and
    you report the parameter estimates (item class probabilities and
    prevalence for all items, asymptotic standard errors).

    -   In the case of 20% and 50% missing data in item 6 you still fit
        the model to all six items and treat the missigness as missing
        at random. since you use ML there should be no problem. you
        should also get estimates for the 6th item that should be close
        to one. is that true? when the gold standard is missing 100%
        then you only estimate parameters for the five items.

5.  The above steps are repeated R times where R is the number of
    replications.

# Performance criteria

We compute the bias and mean squared error (MSE) for each parameter as
follows:$$Bias=\frac{1}{R}\sum_{i=1}^{R}\left(\hat{\theta}_{i}-\theta\right)\:,$$
and
$$MSE=\frac{1}{R}\sum_{i=1}^{R}\left(\hat{\theta}_{i}-\theta\right)^{2}\:,$$
where $R$ here is the number of valid replicates, $\hat{\theta}_{i}$ is
the estimate of a parameter or of its asymptotic standard error at the
$i^{th}$ valid replication, and $\theta$ is the corresponding true
value. In the case of standard errors, where the true value $\theta$ is
unknown, the standard deviation of parameter estimates across valid
replications is used (those are the standard deviations that you report
in the output). My understanding is that you do not compute any
asymptotic standard errors.

***Haziq: The output of the simulations are the MCMC samples of the prevalences, sensitivities and specificities. I am able to compute the posterior mean and posterior standard deviations of these parameters.***

# Presentation of results

-   we can present the bias and MSE of the parameters using graphs and
    in particular lines where each dot on the line will represent an
    item. The x-axis will be the items. the y-axis will be the bias or
    MSE. We do not need to include any confidence levels.

How to present the results: Our aim is to compare the three different
models when each one of those model is true (data generating mechanism)
each time:

***Haziq: I attach the plots in the respective places below***

```{r, include = FALSE, cache = TRUE}
# Plots for bias (sensitivities)
p1 <- plot_paper(res, monitor = "sens", data.gen = "lc")
p2 <- plot_paper(res, monitor = "sens", data.gen = "lcre")
p3 <- plot_paper(res, monitor = "sens", data.gen = "fm")
```
```{r fig1, echo = FALSE, fig.cap = "Bias of parameter estimates (sensitivities) as estimated by the LC, LCRE and FM models under differing proportions of missing gold standard, and under differing data generating mechanisms (n = 250, p = 0.08).", cache = TRUE, fig.pos = "p", fig.height = 12, fig.width = 6, out.height = "0.8\\paperheight", fig.align = "center"}
plot_grid(p1, p2, p3, labels = LETTERS[1:3], ncol = 1)
```

```{r, include = FALSE, cache = TRUE}
# Plots for bias (specificities)
p1 <- plot_paper(res, monitor = "spec", data.gen = "lc")
p2 <- plot_paper(res, monitor = "spec", data.gen = "lcre")
p3 <- plot_paper(res, monitor = "spec", data.gen = "fm")
```
```{r fig2, echo = FALSE, fig.cap = "Bias of parameter estimates (specificities) as estimated by the LC, LCRE and FM models under differing proportions of missing gold standard, and under differing data generating mechanisms (n = 250, p = 0.08).", cache = TRUE, fig.pos = "p", fig.height = 12, fig.width = 6, out.height = "0.8\\paperheight", fig.align = "center"}
plot_grid(p1, p2, p3, labels = LETTERS[1:3], ncol = 1)
```

```{r, include = FALSE, cache = TRUE}
# Plots for MSE (sensitivities)
p1 <- plot_paper(res, monitor = "sens", data.gen = "lc", type = "mse")
p2 <- plot_paper(res, monitor = "sens", data.gen = "lcre", type = "mse")
p3 <- plot_paper(res, monitor = "sens", data.gen = "fm", type = "mse")
```
```{r fig3, echo = FALSE, fig.cap = "MSE of parameter estimates (sensitivities) as estimated by the LC, LCRE and FM models under differing proportions of missing gold standard, and under differing data generating mechanisms (n = 250, p = 0.08).", cache = TRUE, fig.pos = "p", fig.height = 12, fig.width = 6, out.height = "0.8\\paperheight", fig.align = "center"}
plot_grid(p1, p2, p3, labels = LETTERS[1:3], ncol = 1)
```

```{r, include = FALSE, cache = TRUE}
# Plots for MSE (specificities)
p1 <- plot_paper(res, monitor = "spec", data.gen = "lc", type = "mse")
p2 <- plot_paper(res, monitor = "spec", data.gen = "lcre", type = "mse")
p3 <- plot_paper(res, monitor = "spec", data.gen = "fm", type = "mse")
```
```{r fig4, echo = FALSE, fig.cap = "MSE of parameter estimates (specificities) as estimated by the LC, LCRE and FM models under differing proportions of missing gold standard, and under differing data generating mechanisms (n = 250, p = 0.08).", cache = TRUE, fig.pos = "p", fig.height = 12, fig.width = 6, out.height = "0.8\\paperheight", fig.align = "center"}
plot_grid(p1, p2, p3, labels = LETTERS[1:3], ncol = 1)
```

```{r, include = FALSE, cache = TRUE}
# Plots for post. sd (sensitivities)
p1 <- plot_paper(res, monitor = "sens", data.gen = "lc", type = "sd")
p2 <- plot_paper(res, monitor = "sens", data.gen = "lcre", type = "sd")
p3 <- plot_paper(res, monitor = "sens", data.gen = "fm", type = "sd")
```
```{r fig5, echo = FALSE, fig.cap = "Post. SD of parameter estimates (sensitivities) as estimated by the LC, LCRE and FM models under differing proportions of missing gold standard, and under differing data generating mechanisms (n = 250, p = 0.08).", cache = TRUE, fig.pos = "p", fig.height = 12, fig.width = 6, out.height = "0.8\\paperheight", fig.align = "center"}
plot_grid(p1, p2, p3, labels = LETTERS[1:3], ncol = 1)
```

```{r, include = FALSE, cache = TRUE}
# Plots for post. sd (specificities)
p1 <- plot_paper(res, monitor = "spec", data.gen = "lc", type = "sd")
p2 <- plot_paper(res, monitor = "spec", data.gen = "lcre", type = "sd")
p3 <- plot_paper(res, monitor = "spec", data.gen = "fm", type = "sd")
```
```{r fig6, echo = FALSE, fig.cap = "Post. SD of parameter estimates (specificities) as estimated by the LC, LCRE and FM models under differing proportions of missing gold standard, and under differing data generating mechanisms (n = 250, p = 0.08).", cache = TRUE, fig.pos = "p", fig.height = 12, fig.width = 6, out.height = "0.8\\paperheight", fig.align = "center"}
plot_grid(p1, p2, p3, labels = LETTERS[1:3], ncol = 1)
```

***Haziq: Since the true posterior standard deviations are not known, I don't know how to calculate bias and MSE.***

-   Figure 7: MSE of estimated asymptotic standard errors
    (sensitivities), n=250, p=0.04, gold standard=20,40,100,
    Models:LC,LCRE,FM. (total of 9 lines).

-   Figure 8: MSE of estimated asymptotic standard errors
    (specificities), n=250, p=0.04, gold standard=20,40,100,
    Models:LC,LCRE,FM. (total of 9 lines).

The above can be repeated for p=0.80. Figures 1-4 are for bias and MSE
of item class probabilities (sensitivities and specificities) and
Figures 5-8 are for bias and MSE for estimated standard errors.
